Keyword and Collocation analysis on India-related text of *Natural History*

### 2023-08-21 paper_quarto.qmd
0821 methodology update

@@

Since the research focus is narrowed down to India-related text after the initial exploration, a dataset including all Indian place names mentioned in the text is extracted from the geographical-related text dataset. With a reference to *Barrington Atlas of the Greek and Roman World* (@talbert2000a, @talbert2000b), the approximate coordinates defining the Indian region during the time of *Natural Hisoty* are as follows^[As indicated in the map-by-map directory, the range spans territories of “modern states of India (minus the Punjab), Bangladesh, Bhutan, Burma, Nepal, and Sri Lanka”.]:

>Latitude: 5-35 degrees North

>Longitude: 65-95 degrees East

@@

And the full text of the entire work, segregrating in paragraphs, are scraped and stored in TXT format as a **reference corpus**.

@@

# build frequency list for reference corpus
flist_ref <- fnames_wholetext %>%
  freqlist()

# build frequency list for target corpus
flist_target_all <- fnames_indiatext %>%
  freqlist() 
```

The **target corpus** consists of all text related to India in paragraphs, containing `r prettyNum(n_tokens(flist_target_all))` tokens and `r n_types(flist_target_all)` types, with the type-token ratio of `r round(n_types(flist_target_all)/n_tokens(flist_target_all), 2)`.

@@

# build frequency list for target corpus
flist_target <- fnames_indiatext %>%
  freqlist(
    re_token_transf_in = "[[:punct:]]", # Match punctuation marks
    token_transf_out = "", # Replace punctuation marks with an empty string
    re_drop_token = "india"
  )

# build frequency list for reference corpus
flist_ref <- fnames_wholetext %>%
  freqlist(
    re_token_transf_in = "[[:punct:]]", # Match punctuation marks
    token_transf_out = ""
  )

@@

@@

To analyse the co-text surrounding the term "India," the `mclm::surf_cooc()` function was employed, with "india" designated as the target item for the analysis. And following the same criteria as the previous keyword analysis, the collocation scores were filtered of having both PMI and G_signed scores of 2 or higher. By employing this approach, the prominent collocates of "india" were identified, providing a tangible understanding of the prevailing discourse and potentially reflecting Pliny the Elder's perspective on the region.

@@

coocs <- fnames_wholetext %>% 
  surf_cooc("(?xi)  ^ india $", 
            re_token_transf_in = "[[:punct:]]", # Match punctuation marks
            token_transf_out = "")

@@

Furthermore, the concordance table of the word "india" as displayed in @tbl-concordance, presents a comprehensive overview of the instances where "india" appears throughout the text, showcasing the specific contexts as well as providing additional information regarding the references to "India." It serves as a valuable resource for understanding the various perspectives, descriptions, and associations attributed to India within the context of *Natural History*.

```{r}
#| label: tbl-concordance
#| tbl-cap-location: top
#| tbl-cap: Concordance table of word "india" in Natural History
#| warning: false
#| echo: false

conc_data <- conc(fnames_wholetext, '\\bindia\\b')

conc_data %>%
  as_tibble() %>%
  select(source, left, match, right) %>%
  mutate(
    source = short_names(source),
    book = as.integer(gsub("^(\\d+).*", "\\1", source)),
    chapter = as.numeric(gsub("^\\d+\\.(\\d+)\\.\\d+_text$", "\\1", source)),
    paragraph = as.numeric(gsub("^\\d+\\.\\d+\\.(\\d+)_text$", "\\1", source))
  ) %>%
  arrange(book, chapter, paragraph) %>%
  select(book, chapter, paragraph, left, match, right) %>%
  kbl(align = c("r", "r", "r", "c", "l", "l", "l")) %>%
  kable_paper(font_size = 15) %>%
  scroll_box(height = "400px")
```

>>>>

To investigate the prominent themes in the India-related content discussed in *Natural History*, methods of keyword analysis and collocation analysis are employed for this study. Both of the analyses rely on the `mclm::assoc_scores` objects of the [mclm](https://github.com/masterclm/mclm) package, which return frequencies and association scores of a certain event in a target context and in a reference context.

Both of the methods will be examined by three association measurements, namely absolute frequency, PMI and $G^2$ signed, to discuss with the context in *Natural History* and the potential theme it indicates.

PMI measures the association strength between two words by comparing their observed co-occurrence frequency with their expected co-occurrence frequency by chance. It highlights words that appear together more frequently than expected. High PMI values indicates strong associations. High $G^2$ values suggest that the co-occurrence is unlikely to occur by chance.

$G^2$ is a statistical test that measures the independence or association between two categorical variables (words in this case). It compares the observed co-occurrence frequencies with the expected frequencies under the assumption of independence. Higher $G^2$ values suggest a stronger association.

Keyword analysis is a statistical method used in corpus linguistics to identify words that occur more frequently in a target corpus than in a reference corpus. Defined with different associate measurements, the "keyness" of words are calculated and indicated which words are statistically more frequent appeared in the target corpus comparing to that of the reference corpus.

In this study, the *target corpus* includes all paragraphs in *Natural History* mentioning Indian regions, and the **reference corpus** contains all other paragraphs in the work. Lists of 20 words with the highest score in different association measurements are discussed with the textual context. As indicated by the measurements, the listed words tend to be more frequently occur in the context pertaining India than other parts of the work, hence they seem to be the potential keywords about India in *Natural History*.

Collocation analysis is a technique employed in corpus linguistics to identify words that often appear together in a language. This technique is rooted in the notion that particular words tend to appear together more often than would occur by chance. In the context of this study, lists of the highly possible co-occuring word with "India" in the text of *Natural History* can shed a light on the potential themes and topics about India discussed in the work.

Combining the two methods, and integrating with a close reading of the text, this study aims to discuss what about "India" is discussed in *Natural History*.

@@

Since the research focus is narrowed down to India-related text after the initial exploration, a dataset including all Indian place names mentioned in the text is extracted from the geographical-related text dataset. With a reference to *Barrington Atlas of the Greek and Roman World* (@talbert2000a, @talbert2000b), the approximate coordinates defining the Indian region during the time of *Natural Hisoty* are as follows[^3]:

[^3]: As indicated in the map-by-map directory, the range spans territories of "modern states of India (minus the Punjab), Bangladesh, Bhutan, Burma, Nepal, and Sri Lanka".

> Latitude: 5-35 degrees North
>
> Longitude: 65-95 degrees East

@@

And the full text of the entire work, segregating in paragraphs, are scraped and stored in TXT format and excluded the files in **target corpus** to serve as a **reference corpus**.

@@

fnames_wholetext_short <- basename(fnames_wholetext)
fnames_indiatext_short <- basename(fnames_indiatext)

# Exclude short file names with the same name from target corpus in the reference corpus
fnames_wholetext_short_filtered <- fnames_wholetext_short %>%
  setdiff(fnames_indiatext_short)

# Filter full file names based on filtered short names
fnames_wholetext_filtered <- fnames_wholetext[fnames_wholetext_short %in% fnames_wholetext_short_filtered]

# build frequency list for reference corpus
flist_ref <- fnames_wholetext_filtered %>%
  freqlist(re_token_transf_in = "'", 
           token_transf_out = "")

# build frequency list for target corpus
flist_target <- fnames_indiatext %>%
  freqlist(re_token_transf_in = "'", 
           token_transf_out = "") 
```

The **target corpus** consists of all text related to India in paragraphs, containing `r prettyNum(n_tokens(flist_target))` tokens and `r n_types(flist_target)` types, with the type-token ratio of `r round(n_types(flist_target)/n_tokens(flist_target), 2)`.

@@

@@

1.  $G^2$ signed highly overlapped with that of absolute frequency. (plot of corelation)
2.  list the overlapped keywords
3.  PMI sorting provides more information

@@

To analyse the textual collocating bi-gram of word "India", the `mclm::text_cooc()` function was employed, with "india" designated as the target item for the analysis. And following the same criteria as the previous keyword analysis, the collocation scores were filtered of having both PMI and G_signed scores of 2 or higher. By employing this approach, the prominent collocates of "india" were identified, providing a tangible understanding of the prevailing discourse and potentially reflecting Pliny the Elder's perspective on the region.

@@

coocs <- fnames_wholetext %>% 
  text_cooc("(?xi)  ^ india $")

@@
